Fail Faster

### 2025-03-24 paper/paper.tex
abs

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Property-based testing relies on random input generators to uncover bugs, often under tight time constraints. These generators are built 
  using generator libraries, which provide expressive combinators for constructing complex inputs. 
  Although convenient,
  today's generator libraries suffer from substantial performance costs, limited by abstraction overhead and inefficient randomness libraries.
  In this paper, we identify and address these bottlenecks. We introduce \name, a multi-stage programming technique that eliminates generator overhead
  without sacrificing the flexibility and expressiveness of existing generator library functions. We augment leading generator libraries in OCaml and 
  Scala 3 to use the \name approach, preserving the original library's semantics and enabling precise performance comparisons. We also show that \rand
  has a measurable impact on generator performance, quantify its contribution, and show that speedups of $5.5\times$ are possible. Together, these contributions
  lead to up to $13\times$ faster bug finding, showing that high-level generator abstractions need not come at the cost of speed.
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Property-based testing relies on random input generators to uncover bugs, often under tight time constraints. These generators are built 
  using generator libraries, which provide expressive combinators for constructing complex inputs. 
  Although convenient,
  today's generator libraries suffer from substantial performance costs, limited by abstraction overhead and inefficient randomness libraries.
  In this paper, we identify and address these bottlenecks. We introduce \name, a multi-stage programming technique that eliminates generator overhead
  without sacrificing the flexibility and expressiveness of existing generator library functions. We augment leading generator libraries in OCaml and 
  Scala 3 to use the \name approach, preserving the original library's semantics and enabling precise, pointwise performance comparisons. We also show that \rand
  has a measurable impact on generator performance, quantify its contribution, and show that speedups of $5.5\times$ are possible. Together, these 
  improvements lead to bug-finding up to $13\times$ faster---showing that high-level generator abstractions need not come at the cost of speed.
\end{abstract}
